---
title: "Lab 09 - Grading the professor, Pt. 1"
author: "Fiona Wang"
date: "Mar-20-2025"
output: github_document
---

## Load Packages and Data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(tidymodels)
library(openintro)
```

## Exercise 1

```{r loaddata}
data <- evals
```

```{r scorehist, message = FALSE}
data %>% 
  ggplot(aes(x = score)) + geom_histogram(binwidth = 0.1, color = "black")
```

As we can see from the graph, the majority of the data is on the right, and the tail extends to the left. Thus it is left-skewed. It doesn't show me a lot of details about students' rate. I want to include a boxplot and the summary statistics here too. 
```{r scorebox}
data %>% 
  ggplot(aes(y = score)) + geom_boxplot()
summary(data$score)
```

The mean rating is 4.18. Students were, on average, pretty satisfied with their professors. With a max of 5, and a min of 2.3. There are also 3 outliers on the lower end according to the boxplot. This is what I expected. Students rated on 463 courses taught by 94 professors, so I expected this variance. I think an average of 4.18 is fair and pretty good. 

## Exercise 2

*Provide your answer here.*  
Add code chunks as needed.

```{r exercise2_code}
# Add your R code here
```

## Additional Exercises

*Repeat the format above for additional exercises.*

## Hint

For Exercise 12, the `relevel()` function can be helpful!
